\chapter*{Introduction}

This document is the project report for the Database course at the Department of Computer Science, University of Bari Aldo Moro.

The project is about designing and building a database for a company called ConferenceHub Inc. that manages academic conferences. The document is divided into chapters: requirements analysis, conceptual design (ER), logical design, physical implementation in Oracle SQL, web application, and a bonus chapter on data warehousing.

\section*{Box Types Used in This Document}

In this document we use colored boxes to separate different types of content. Each color has a specific meaning:

\begin{itemize}[itemsep=6pt]
    \item \textbf{\textcolor{green!50!black}{Green} --- Specifications.} Text taken directly from the original requirements.

    \item \textbf{\textcolor{violet!55!black}{Violet} --- Assumption / Design Reasoning.} Explains a design choice or an assumption we made.

    \item \textbf{\textcolor{blue!55!black}{Blue} --- Info.} Extra context or useful notes.

    \item \textbf{\textcolor{black!45}{Grey} --- SQL Code.} SQL code with syntax highlighting.
\end{itemize}

Here is an example of each box:

\begin{tracebox}
This is a green Specifications box. It shows text taken from the requirements.
\end{tracebox}

\begin{reasoningbox}
This is a violet Assumption / Design Reasoning box. It explains a design decision or an assumption.
\end{reasoningbox}

\begin{infobox}
This is a blue Info box. It gives additional context or clarifications.
\end{infobox}

\begin{highlightbox}
This is a grey highlight box, used for short formulas or patterns worth remembering.
\end{highlightbox}
